\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{casual}
\moderncvcolor{blue}

\usepackage[scale=0.75]{geometry}
\usepackage{enumitem}

\name{Igor}{Gabaydulin}
\title{Curriculum Vitae}
\address{Moscow, Russia}{Phuket, Thailand (Present)}
\email{igabaydulin@gmail.com}

\social[github]{igabaydulin}
\social[linkedin]{igabaydulin}
\social[twitter]{igabaydulin}
\quote{Weeks of coding can save you hours of planning.}

\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}

\begin{document}
\makecvtitle

\section{Experience}
\subsection{Vocational}
\cventry{2021--2023}{Senior Software Engineer}{Revolut}{Moscow}{Product · Retail · Banking · Topup \& Open Banking}
{
Lead backend developer in cross-functional team supervising two backend developers. Work on the design and implementation of interbank interactions (Open Banking) for account topups. Better user experience with less number of required interbank actions leading to increased topup acceptance rate. Intercommunication with vendors for new integrations and Open Banking features. 
\newline
\newline
Implementation of asynchronous persistent aggregator and localised report provider on top of CQRS framework and event driven system model with caching and rate limiting. To keep up with increasing number of functional requirements functional tests were designed that helped speed up the process of requirements verification, bug detection, and prototyping.
\newline
\newline
Found an \href{https://github.com/scala/bug/issues/12586}{\underline{\color{blue}issue}} in Scala's \texttt{ConcurrentMap} implementation (\href{https://medium.com/@igabaydulin/java-concurrenthashmap-vs-scala-concurrent-map-e185e8a0b798}{\underline{\color{blue}Medium article}} about investigation, benchmarks and fix).
\begin{itemize}
\item Java 11, Java 17, Groovy, Kotlin, Gradle, Checkstyle, JOOQ
\item PostgreSQL, Redis
\item Docker, Kubernetes, Google Cloud, TestContainers
\item TeamCity
\item New Relic, Grafana
\end{itemize}
}
\cventry{2020--2021}{Senior Software Development Engineer}{Deutsche Bank}{Moscow}{Commercial Banking Services IT Division}
{
Service orchestration implementation in Deutsche Bank payment system to handle and proxy payments (including ISO20022). Design and implementation of orchestrator load balancer supporting multithreading, back pressure, affinity checks, retries, dead letter queues. MQ and Kafka integration. Message bridge implementation from MQ to Kafka. Candidates interviewing, onboarding and mentoring.
\begin{itemize}
\item Java 8, Java 11, Maven, JIB, Checkstyle, Jacoco
\item Spring, Spring Boot, Spring Cloud
\item JUnit Jupiter, AssertJ, Cucumber
\item Oracle RDBMS
\item Kafka, IBM MQ, Consul
\item Docker, Kubernetes, helm
\item Sonar, Jenkins, TeamCity
\item Geneos
\end{itemize}
}
\cventry{2019--2020}{Lead Software Developer}{Evotor}{Moscow}{Cloud Management Department}{
Supervised a team of three backend developers maintaining an application marketplace for smart terminals (cash registers). Design, implementation and management of more than 30 microservices, release and test flow improvements.\\\\
Debezium integration to force eventual consistency with PostgreSQL and Kafka. Found, investigated and fixed an issue in Debezium preventing Patroni failovers (\href{https://github.com/debezium/debezium/pull/1219}{\underline{\color{blue}DBZ-1727}}).
\begin{itemize}
\item Java 8, Java 11, Java 12, Gradle
\item Spring 5, Spring Boot 2, Spring Cloud
\item JUnit 5, Testcontainers
\item PostgreSQL, ClickHouse, Redis
\item Kafka, Zookeeper, Debezium
\item Docker, Kubernetes, helm
\item Kibana, ElasticSearch, JavaMelody, Zabbix, Prometheus, Grafana
\end{itemize}
}
\cventry{2018--2019}{Senior Software Developer}{Evotor}{Moscow}{Cloud Management Department}{
Migration from Docker Compose to Kubernetes and helm. Cache optimisations and usage of external cache Redis for multiple pods. Heap dump profilings, fixing memory leaks caused by asynchronous Logback appenders.
\\\\
Implementation of custom metrics with micrometer, prometheus and Grafana. Implementation of custom Jenkins pipelines. Helping QA testers to design automated tests.
\begin{itemize}
\item Java 8, Gradle
\item Spring 4. Spring Boot 1, Spring Cloud
\item JUnit 4, Mockito
\item PostgreSQL, Redis
\item Docker, Kubernetes, helm
\item Kibana, ElasticSearch, Javamelody, Zabbix, Prometheus, Grafana
\item Kafka, Zookeeper
\end{itemize}
}
\cventry{2017--2018}{Software Developer}{Evotor}{Moscow}{Cloud Management Department}{Maintenance of a dozen microservices, implementation and design for a couple of new microservices such as app rating service and targeting service. Common libraries implementation that were used across multiple microservices.
\begin{itemize}
\item Java 8, Gradle
\item Spring 4, Spring Boot 1, Spring Cloud
\item JUnit 4, Mockito
\item PostgreSQL
\item Kafka, Zookeeper
\item Docker, docker-compose, docker registry
\item Kibana, ElasticSearch, Javamelody, Zabbix
\end{itemize}}
\cventry{2016--2017}{Backend Developer}{VibrantFire}{Moscow}{Startup Project}{Work in a little startup project started by students of Moscow State University. Design and implementation of a few monolithic Web servers.
\begin{itemize}
\item Java 7, Maven
\item Spring, Spring Boot, Hibernate, Tomcat
\item JUnit 4, Mockito
\item Database: PostgreSQL
\end{itemize}}
\cventry{2014--2015}{Junior Developer}{
Ivannikov Institute for System Programming of the RAS}{Moscow}{}{Text analysis tool. Removal of cyclic dependencies between terms.}

\newpage
\section{Languages}
\cvitemwithcomment{Russian}{Native}{}
\cvitemwithcomment{English}{Upper Intermediate}{}

\section{Computer skills}
\cvdoubleitem{Programming}{Java, Kotlin, Groovy, Scala}{Databases}{PostgreSQL}
\cvdoubleitem{OS}{MacOS, Linux, Windows}{Other}{Kafka, Redis, zookeeper}
\cvitem{Containers}{Docker, Kubernetes, GCP, OpenShift, helm}

\section{Interests}
\cvitem{Programming}{In school I studied Pascal and Delphi. At Higher School of Economics university I studied C\# and Java. Had a fun time with computer vision and computational geometry courses. At Moscow State University had some fun in sports programming. Like to implement some algos or data structures from time to time.}
\cvitem{Music}{Love to play the piano.}

\section{Extra}
\cvlistitem{Not a big fan of Spring Framework. Good for prototyping but may blur your eyes hiding important functional details under framework juice. Still a powerful tool in good hands. The same goes to Mokito. Cannot implement a test without Mokito? Something may be wrong with the design choices.}
\cvlistitem{Anemic objects are evil. It contradicts with OOP. Maybe FP is the way to go.}

\clearpage
\end{document}